---
  title: "Advertising"
output:
  word_document: default
pdf_document: default
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Data 

```{r}

# Clear All Variables & Clear the Screen
rm(list=ls())
cat("\014")

# Read in the Data
data.ad = read.csv("/Users/jadechen/Documents/Customer/AD/Ex3_Data_R.csv")

# Explore the data
str(data.ad )
summary(data.ad )
```

## PREPARE DATA

In our case we have to create new variables: log(Advertising), Advertising^2, and Lag(Sales)

```{r}

# Create log Advertising (we have done this for price so look it up!)
data.ad$logTotal.Spent <- log(data.ad$Total.Spent)

# Create Advertising^2
data.ad$Total.Spent2 <- (data.ad$Total.Spent)^2

# Create LAG Sales
data.ad$LagVisitors <- c(NA, head(data.ad$Visitors, -1))

# Display the data
summary(data.ad)
```

## REGRESSION MODELS

1) Define y (Dependent Variable). For this example, we have Y (e.g., sales).

2) Define X (Independent Variables). For this example, we have X1, X2 and X3 (some marketing measures, e.g., price, advertising)

3) Run the Models. For example, a linear model where Sales (Y) is a function of X1, X2 and X3

```{r}

# Run the Regression (includes an INTERCEPT)
lm.model1 <- lm(Visitors ~ Total.Spent, data = data.ad)
lm.model2 <- lm(Visitors ~ logTotal.Spent, data = data.ad)
lm.model3 <- lm(Visitors ~ Total.Spent + Total.Spent2, data = data.ad)

lm.model1a <- lm(Visitors ~ Total.Spent + LagVisitors , data = data.ad)
lm.model2a <- lm(Visitors ~ logTotal.Spent + LagVisitors , data = data.ad)
lm.model3a <- lm(Visitors ~ Total.Spent + Total.Spent2 + LagVisitors , data = data.ad)

# Display Results
summary(lm.model1)
summary(lm.model2)
summary(lm.model3)

summary(lm.model1a)
summary(lm.model2a)
summary(lm.model3a)
```

##calculate elasticity
```{r}
#Average Visitor for July
avg.julvisitor<- mean(data.ad$Visitors[62:66])

#Average Spending for July
avg.julspending<- mean(data.ad$Total.Spent[62:66])
```
#Model 1 elasticity
```{r}
beta1= lm.model1$coefficients
t_stat1 = coef(summary(lm.model1))[,3]

#check for statistical significance
beta.sig1 = beta1;

for (i in length(beta1)){
  if(abs(t_stat1[i])<1.96) {
    beta.sig1[i]=0}
}
#calculate elasticity
model1_elasticity<- beta.sig1[2] * (avg.julspending/avg.julvisitor)
model1_elasticity
```
#Model 2 elasticity
```{r}
#Get model 2 coefficient
beta2= lm.model2$coefficients
t_stat2 = coef(summary(lm.model2))[,3]

#check for statistical significance
beta.sig2 = beta2;

for (i in length(beta2)){
  if(abs(t_stat2[i])<1.96) {
    beta.sig2[i]=0}
}
#calculate elasticity
model2_elasticity<- beta.sig2[2] * (1/avg.julvisitor)
model2_elasticity
```
#Model 3 elasticity
```{r}
#Get model 3 coefficient
beta3= lm.model3$coefficients
t_stat3 = coef(summary(lm.model3))[,3]

#check for statistical significance
beta.sig3 = beta3;

for (i in length(beta3)){
  if(abs(t_stat3[i])<1.96) {
    beta.sig3[i]=0}
}
#calculate elasticity
model3_elasticity<- (beta.sig3[2] +2*beta.sig3[3]*(avg.julspending))*(avg.julspending/avg.julvisitor)
model3_elasticity
```
#Model 1a elasticity
```{r}
#Get model 1a coefficient
beta4= lm.model1a$coefficients
t_stat4 = coef(summary(lm.model1a))[,3]

#check for statistical significance
beta.sig4 = beta4;

for (i in length(beta4)){
  if(abs(t_stat4[i])<1.96) {
    beta.sig4[i]=0}
}
#calculate elasticity
model1a_elasticity<- (beta.sig4[2]/(1-beta.sig4[3]))*(avg.julspending/avg.julvisitor)
model1a_elasticity
beta.sig4[2]
```
#Model2a elasticity
```{r}
#Get model 2a coefficient
beta5= lm.model2a$coefficients
t_stat5 = coef(summary(lm.model2a))[,3]

#check for statistical significance
beta.sig5 = beta5;

for (i in length(beta5)){
  if(abs(t_stat5[i])<1.96) {
    beta.sig5[i]=0}
}
#calculate elasticity
model2a_elasticity<- (beta.sig5[2]/(1-beta.sig5[3]))* (1/avg.julvisitor)
model2a_elasticity
```
#Model3a elasticity
```{r}
#Get model 3a coefficient
beta6= lm.model3a$coefficients
t_stat6 = coef(summary(lm.model3a))[,3]

#check for statistical significance
beta.sig6 = beta6;

for (i in length(beta6)){
  if(abs(t_stat6[i])<1.96) {
    beta.sig6[i]=0}
}
#calculate elasticity
model3a_elasticity<- ((beta.sig6[2] +2*beta.sig6[3]*(avg.julspending))/(1-beta.sig6[4]))*(avg.julspending/avg.julvisitor)
model3a_elasticity
```

#Saturation
#Saturation for model 3
```{r}
#Saturation for model 3
model3.sat<- -beta.sig3[2]/2*beta.sig3[3]
model3.sat
```
#Saturation for model 3a
```{r}
#Saturation for model 3a
model3a.sat<- -beta.sig6[2]/2*beta.sig6[3]
model3a.sat

```